FMA: A Dataset For Music Analysis

### 2017-04-25 fma.tex
non-anonymous output

\newcommand{\ntracks}{106,574 }
\newcommand{\nartists}{16,341 }
\newcommand{\nalbums}{14,854 }
\newcommand{\ngenres}{161 }
\newcommand{\tduration}{343 }
\newcommand{\aduration}{278 }
\newcommand{\size}{917 }
%\newcommand{\weblink}{https://github.com/mdeff/fma}
\newcommand{\weblink}{http://164.132.40.229/fma}

@@

\multauthor
{\phantom{Michaël Defferrard$^*$ \hspace{.6cm} Kirell Benzi$^*$ \hspace{.6cm} Pierre Vandergheynst$^*$ \hspace{.6cm} Xavier Bresson$^\dagger$}}
{\phantom{
	$^*$LTS2, EPFL, Lausanne, Switzerland \hspace{0.4cm}
	$^\dagger$SCSE, NTU, Singapore \hspace{0.4cm}
	{\small Work conducted when XB was at EPFL.}}\\
	\phantom{\tt\small \{michael.defferrard,kirell.benzi,pierre.vandergheynst\}@epfl.ch, xbresson@ntu.edu.sg}
  }

@@

\phantom{
We want to thank the team supporting the \href{https://freemusicarchive.org}{Free Music Archive} as well as all the contributing artists and curators for the fantastic content they made available.
We are grateful to SWITCH and EPFL for hosting the dataset within the context of the \href{https://projects.switch.ch/scale-up}{SCALE-UP} project, funded in part by the swissuniversities \href{http://www.swissuniversities.ch/isci}{SUC P-2 program}.
% We are grateful to \href{https://zenodo.org}{zenodo.org}, whose free hosting and archiving of digital research artifacts is promoting a more open scientific process.
Xavier Bresson is supported by NRF Fellowship NRFF2017-10.
}

>>>>

\newcommand{\ntracks}{106,574 }
\newcommand{\nartists}{16,341 }
\newcommand{\nalbums}{14,854 }
\newcommand{\ngenres}{161 }
\newcommand{\tduration}{343 }
\newcommand{\aduration}{278 }
\newcommand{\size}{917 }
\newcommand{\weblink}{https://github.com/mdeff/fma}
%\newcommand{\weblink}{http://164.132.40.229/fma}

@@

\multauthor
{Michaël Defferrard$^*$ \hspace{.6cm} Kirell Benzi$^*$ \hspace{.6cm} Pierre Vandergheynst$^*$ \hspace{.6cm} Xavier Bresson$^\dagger$}
{
	$^*$LTS2, EPFL, Lausanne, Switzerland \hspace{0.4cm}
	$^\dagger$SCSE, NTU, Singapore \hspace{0.4cm}
	{\small Work conducted when XB was at EPFL.}\\
	{\tt\small \{michael.defferrard,kirell.benzi,pierre.vandergheynst\}@epfl.ch, xbresson@ntu.edu.sg}
  }

@@

We want to thank the team supporting the \href{https://freemusicarchive.org}{Free Music Archive} as well as all the contributing artists and curators for the fantastic content they made available.
We are grateful to SWITCH and EPFL for hosting the dataset within the context of the \href{https://projects.switch.ch/scale-up}{SCALE-UP} project, funded in part by the swissuniversities \href{http://www.swissuniversities.ch/isci}{SUC P-2 program}.
% We are grateful to \href{https://zenodo.org}{zenodo.org}, whose free hosting and archiving of digital research artifacts is promoting a more open scientific process.
Xavier Bresson is supported by NRF Fellowship NRFF2017-10.
